Looking at Non-Linear Dimension Reductions as Models in the Data Space

### 2024-09-29 paper.qmd
Updated Figure 10

trimesh_two_curvy2 <- ggplot() +
  geom_segment(data = tr_from_to_df_two_curvy2,
               aes(
                 x = x_from,
                 y = y_from,
                 xend = x_to,
                 yend = y_to),
               colour = "#33a02c") +
  interior_annotation("a", position = c(0.92, 0.95))

@@

benchmark_two_curvy <- 1.3

@@

trimesh_two_curvy_removed2 <- ggplot() +
  geom_segment(data = tr_from_to_df_two_curvy4,
               aes(
                 x = x_from,
                 y = y_from,
                 xend = x_to,
                 yend = y_to),
               colour = "#33a02c") +
  interior_annotation("b", position = c(0.92, 0.95))

@@

```{r}
#| fig-width: 6
#| fig-height: 4
#| fig-cap: "long edge removal"

>>>>

trimesh_two_curvy2 <- ggplot() +
  geom_segment(data = tr_from_to_df_two_curvy2,
               aes(
                 x = x_from,
                 y = y_from,
                 xend = x_to,
                 yend = y_to),
               colour = "#000000") +
  interior_annotation("a", position = c(0.92, 0.95))

@@

benchmark_two_curvy <- 0.42

@@

trimesh_two_curvy_removed2 <- ggplot() +
  geom_segment(data = tr_from_to_df_two_curvy4,
               aes(
                 x = x_from,
                 y = y_from,
                 xend = x_to,
                 yend = y_to),
               colour = "#000000") +
  interior_annotation("b", position = c(0.92, 0.95))

@@

```{r}
#| fig-width: 9
#| fig-height: 2
#| fig-cap: "long edge removal"
